Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Add a note
Extend "Open problems and future work"

@@

SmallCheck~\cite{smallcheck} is a tool for
automatic exhaustive testing at a certain level.
Both Doctest and Hspec do not have support for SmallCheck
at this moment.

>>>>

\subsection{Source locations for failing examples}

TBD:

We do not get source locations for failing tests. Doctest solves this.
For Hspec/QuickCheck/HUnit something like JHC's
\verb|SRCLOC_ANNOTATE|
pragma~\cite{todo}
could help.

\begin{quote}
    sol: @kazu should we cite
    \url{http://repetae.net/computer/jhc/jhc.shtml}?
\end{quote}

@@

SmallCheck~\cite{smallcheck} is a tool for
automatic exhaustive testing at a certain level.
Both Doctest and Hspec do not have support for SmallCheck
at this moment.
\begin{itemize}
    \item
        \emph{sol: Hspec's mechanism for evidence is extensible.  It
        would be easy to add support for SmallCheck.}
\end{itemize}
